### 2015-05-24 docs/report/code_sharing.tex
Adds report benchmark for shared function transfer vs serialization.

>>>>

\subsubsection{\tstring{} serialization and shared tranfer benchmark}

We created a benchmark that compares these two scenarios:

\begin{enumerate}
\item Sending the \tstring{} representation of a function to four Web Workers.
\item Encoding a function into a \tsabuffer{} and sending it to four Web Workers.
\end{enumerate}

The code for the benchmark is presented in the following code listing:
\bmcode{http://jsperf.com/shared-function-transfer}{../../spikes/shared/2.2.1/jspBenchmark.longSendCode.js}

The results for it are displayed in Figure~\ref{fig:serialization-vs-shared-transfer}.
\img{Comparing string serialization vs shared buffer transfer approaches}{../../spikes/shared/2.2.1/jspBenchmarklongSendCode.png}{fig:serialization-vs-shared-transfer}
